Are rankings of financial analysts useful to investors?

### 2015-03-12 doc/paper/paper-knitr-APS.tex
all tables per APS

\usepackage{alltt}
\usepackage{fancyhdr}
\usepackage{time}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
%\usepackage{rotating}
%\usepackage{xcolor}
\usepackage[hyphens]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
%\usepackage{breakurl}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
%\onehalfspacing
\doublespace
\usepackage[longnamesfirst]{natbib}
%\usepackage[natbibapa,longnamesfist]{apacite}

@@

Table \ref{tab:stocks} shows the number of active stocks for each of the trading strategies (\textit{CONS},\textit{TP},\textit{EPS}) conditional on considered information sets.
%obtained from the rankings based on the target price accuracy. We observe a reduction in average per stock expected return with the mean of  round(rank.views.full.period['true','mean'],3)*100\%. The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of  round(pt.eps.rank.views.full.period['true','mean'],3)*100\%. Overall, compared to the consensus, both ranking-based methods exhibit less optimistic expected returns and are pretty close to the historical averages.

@@

\begin{tabularx}{\linewidth}{r*{6}{Y}}
    \toprule
Year & Min& Mean & Median &Max& Std.dev\\
\midrule
%Panel A: TP&&&&&\\
\multicolumn{6}{c}{\textbf{Panel A: TP}} \\
\midrule
%Year & Min& Mean & Median &Max& Std.dev\\
 1999 & 3.00 & 4.25 & 4 &  10 & 1.59 \\ 
  2000 & 3.00 & 4.76 & 4 &  14 & 1.88 \\ 
  2001 & 3.00 & 5.25 & 5 &  15 & 2.32 \\ 
  2002 & 3.00 & 6.04 & 5 &  19 & 2.95 \\ 
  2003 & 3.00 & 6.67 & 6 &  21 & 3.43 \\ 
  2004 & 3.00 & 7.12 & 6 &  21 & 3.62 \\ 
  2005 & 3.00 & 7.35 & 7 &  21 & 3.59 \\ 
  2006 & 3.00 & 7.41 & 7 &  20 & 3.42 \\ 
  2007 & 3.00 & 7.05 & 6 &  20 & 3.33 \\ 
  2008 & 3.00 & 6.37 & 6 &  18 & 2.88 \\ 
  2009 & 3.00 & 5.15 & 5 &  18 & 2.19 \\ 
   \midrule 
Total & 3.00 & 6.42 & 6 &  21 & 3.21 \\

@@

\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multicolumn{6}{c}{\textbf{Panel B: EPS}} \\
\midrule
 1999 & 3.00 & 5.73 & 5 &  17 & 3.01 \\ 
  2000 & 3.00 & 5.43 & 5 &  17 & 2.77 \\ 
  2001 & 3.00 & 6.02 & 5 &  18 & 2.97 \\ 
  2002 & 3.00 & 6.34 & 5 &  21 & 3.26 \\ 
  2003 & 3.00 & 6.52 & 6 &  24 & 3.43 \\ 
  2004 & 3.00 & 6.95 & 6 &  22 & 3.75 \\ 
  2005 & 3.00 & 7.21 & 6 &  24 & 3.77 \\ 
  2006 & 3.00 & 7.49 & 7 &  26 & 3.84 \\ 
  2007 & 3.00 & 7.13 & 6 &  21 & 3.53 \\ 
  2008 & 3.00 & 6.38 & 6 &  22 & 3.06 \\ 
  2009 & 3.00 & 5.81 & 5 &  20 & 2.78 \\ 
   \midrule 
Total & 3.00 & 6.58 & 6 &  26 & 3.43 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Secnario& Mean (in \%) & Median (in \%) &Std.dev\\
\midrule
  \multicolumn{4}{l}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & 18.577 & 16.861 & 0.119 \\ 
  \naive{} & 18.615 & 16.866 & 0.120 \\ 
  \default{} & 21.729 & 20.478 & 0.102 \\

@@

\begin{table}[hp]
  \caption{Number of active stocks}
  \label{tab:stocks}
\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C). 
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Year& $CONS$& $PT$ &$EPS$\\
\midrule
  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 &  219 &  219 &  144 \\ 
  2000 &  295 &  295 &  211 \\ 
  2001 &  341 &  341 &  257 \\ 
  2002 &  374 &  374 &  299 \\ 
  2003 &  390 &  390 &  311 \\ 
  2004 &  399 &  399 &  331 \\ 
  2005 &  414 &  414 &  343 \\ 
  2006 &  421 &  421 &  344 \\ 
  2007 &  426 &  426 &  357 \\ 
  2008 &  420 &  420 &  339 \\ 
  2009 &  365 &  365 &  300 \\ 
   \midrule 
Total &  442 &  442 &  376 \\

@@

\begin{table}[hp]
  \caption{Trading strategies performance: entire period}
  \label{tab:strategy}
  \ This table shows the performance statistics of the different trading strategies. Panel A presents the results for the passive strategy. Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}); and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates . Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking. The trading period goes from 2000Q1 until 2009Q4.

@@

\begin{table}[hp]
  \caption{Trading strategies performance: sub-periods}
  \label{tab:substrategy}
  \ This table presents the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods. Panel A represents the perfect foresight information set; panels B and C show, respectively, the results of the strategies using the most recent and all history analysts' performance. 
\begin{tabularx}{\linewidth}{r*{5}{Y}}
\toprule
  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
Period&\textit{Market}&\textit{CONS}&\textit{TP}&\textit{EPS} \\  \multicolumn{5}{l}{\textbf{Panel A: \tr{}}} \\
2000Q1/2004Q4 & -0.201 & 0.287 & 0.447 & 0.232 \\ 
  2001Q1/2005Q4 & -0.093 & 0.261 & 0.477 & 0.311 \\ 
  2002Q1/2006Q4 & 0.196 & 0.485 & 0.794 & 0.540 \\ 
  2003Q1/2007Q4 & 0.925 & 1.201 & 1.844 & 1.299 \\ 
  2004Q1/2008Q4 & -0.435 & -0.233 & 0.136 & -0.173 \\ 
  2005Q1/2009Q4 & -0.158 & -0.042 & 0.242 & 0.011 \\ 
  All period & -0.182 & 0.125 & 0.351 & 0.123 \\

\midrule
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel B: \naive{}}} \\
2000Q1/2004Q4 & -0.201 & 0.168 & 0.169 & 0.072 \\ 
  2001Q1/2005Q4 & -0.093 & 0.171 & 0.215 & 0.167 \\ 
  2002Q1/2006Q4 & 0.196 & 0.448 & 0.492 & 0.453 \\ 
  2003Q1/2007Q4 & 0.925 & 1.105 & 1.246 & 1.152 \\ 
  2004Q1/2008Q4 & -0.435 & -0.344 & -0.306 & -0.332 \\ 
  2005Q1/2009Q4 & -0.158 & -0.146 & -0.126 & -0.106 \\ 
  All period & -0.182 & 0.008 & 0.018 & -0.020 \\

\midrule
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -0.201 & 0.247 & 0.233 & 0.276 \\ 
  2001Q1/2005Q4 & -0.093 & 0.230 & 0.252 & 0.283 \\ 
  2002Q1/2006Q4 & 0.196 & 0.430 & 0.469 & 0.490 \\ 
  2003Q1/2007Q4 & 0.925 & 0.876 & 0.962 & 0.970 \\ 
  2004Q1/2008Q4 & -0.435 & -0.439 & -0.415 & -0.403 \\ 
  2005Q1/2009Q4 & -0.158 & -0.235 & -0.210 & -0.193 \\ 
  All period & -0.182 & -0.004 & -0.000 & 0.028 \\

>>>>

\usepackage{alltt}
\usepackage{fancyhdr}
\usepackage{time}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
%\usepackage{rotating}
%\usepackage{xcolor}
\usepackage[hyphens]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
%\usepackage{breakurl}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{adjustbox}
%\onehalfspacing
\doublespace
\usepackage[longnamesfirst]{natbib}
%\usepackage[natbibapa,longnamesfist]{apacite}

@@

Table \ref{tab:stocks} shows the number of active stocks for each of the trading strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) conditional on considered information sets.
%obtained from the rankings based on the target price accuracy. We observe a reduction in average per stock expected return with the mean of  round(rank.views.full.period['true','mean'],3)*100\%. The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of  round(pt.eps.rank.views.full.period['true','mean'],3)*100\%. Overall, compared to the consensus, both ranking-based methods exhibit less optimistic expected returns and are pretty close to the historical averages.

@@

\begin{tabularx}{\linewidth}{r*{6}{Y}}
    \toprule
Year & Min& Mean & Median &Max& Std.dev\\
\midrule
%Panel A: TP&&&&&\\
\multicolumn{6}{c}{\textbf{Panel A: TP}} \\
\midrule
%Year & Min& Mean & Median &Max& Std.dev\\
 1999 &    3 & 4.246 & 4 &   10 & 1.588 \\ 
  2000 &    3 & 4.756 & 4 &   14 & 1.878 \\ 
  2001 &    3 & 5.248 & 5 &   15 & 2.323 \\ 
  2002 &    3 & 6.043 & 5 &   19 & 2.948 \\ 
  2003 &    3 & 6.667 & 6 &   21 & 3.427 \\ 
  2004 &    3 & 7.120 & 6 &   21 & 3.617 \\ 
  2005 &    3 & 7.348 & 7 &   21 & 3.592 \\ 
  2006 &    3 & 7.408 & 7 &   20 & 3.417 \\ 
  2007 &    3 & 7.050 & 6 &   20 & 3.334 \\ 
  2008 &    3 & 6.370 & 6 &   18 & 2.884 \\ 
  2009 &    3 & 5.152 & 5 &   18 & 2.191 \\ 
   \midrule 
Total &    3 & 6.421 & 6 &   21 & 3.210 \\

@@

\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multicolumn{6}{c}{\textbf{Panel B: EPS}} \\
\midrule
 1999 &    3 & 5.728 & 5 &   17 & 3.007 \\ 
  2000 &    3 & 5.433 & 5 &   17 & 2.774 \\ 
  2001 &    3 & 6.020 & 5 &   18 & 2.972 \\ 
  2002 &    3 & 6.338 & 5 &   21 & 3.264 \\ 
  2003 &    3 & 6.523 & 6 &   24 & 3.430 \\ 
  2004 &    3 & 6.947 & 6 &   22 & 3.749 \\ 
  2005 &    3 & 7.205 & 6 &   24 & 3.774 \\ 
  2006 &    3 & 7.494 & 7 &   26 & 3.843 \\ 
  2007 &    3 & 7.134 & 6 &   21 & 3.532 \\ 
  2008 &    3 & 6.378 & 6 &   22 & 3.062 \\ 
  2009 &    3 & 5.811 & 5 &   20 & 2.783 \\ 
   \midrule 
Total &    3 & 6.582 & 6 &   26 & 3.426 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
& Mean (in \%) & Median (in \%) &Std.dev\\
\midrule
  \multicolumn{4}{l}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & 18.577 & 16.861 & 0.119 \\ 
  \naive{} & 18.615 & 16.866 & 0.120 \\ 
  \default{} & 21.729 & 20.478 & 0.102 \\

@@

\begin{table}[hp]
  \caption{Number of active stocks}
  \label{tab:stocks}
\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C). 
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Year& \textit{CONS}& \textit{TP} & \textit{EPS}\\
  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 &  219 &  219 &  144 \\ 
  2000 &  295 &  295 &  211 \\ 
  2001 &  341 &  341 &  257 \\ 
  2002 &  374 &  374 &  299 \\ 
  2003 &  390 &  390 &  311 \\ 
  2004 &  399 &  399 &  331 \\ 
  2005 &  414 &  414 &  343 \\ 
  2006 &  421 &  421 &  344 \\ 
  2007 &  426 &  426 &  357 \\ 
  2008 &  420 &  420 &  339 \\ 
  2009 &  365 &  365 &  300 \\ 
   \midrule 
Total &  442 &  442 &  376 \\

@@

\begin{table}[hp]
  \caption{Trading strategies performance: entire period}
  \label{tab:strategy}
  \ This table shows the performance statistics of the different trading strategies. Panel A presents the results for the passive strategy. Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}) and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates . Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking. The trading period goes from 2000Q1 until 2009Q4.

@@

\begin{table}[hp]
  \caption{Trading strategies performance: sub-periods}
  \label{tab:substrategy}
  \ This table presents the annualized return (in \%) and the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods. Panel A represents the perfect foresight information set; panels B and C show, respectively, the results of the strategies using the most recent and all history analysts' performance.

\resizebox{\textwidth}{!}{%
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
\begin{tabular}{rrrrrrrrr}
\toprule
Period&\multicolumn{2}{c}{\textit{Market}}&\multicolumn{2}{c}{\textit{CONS}}&\multicolumn{2}{c}{\textit{TP}}&\multicolumn{2}{c}{\textit{EPS}} \\

& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR\\

  \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 4.476 & 0.287 & 6.780 & 0.447 & 3.577 & 0.232 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.948 & 0.261 & 6.937 & 0.477 & 4.558 & 0.311 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 6.201 & 0.485 & 9.785 & 0.794 & 6.455 & 0.540 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 10.432 & 1.201 & 14.850 & 1.844 & 10.713 & 1.299 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -2.931 & -0.233 & 1.676 & 0.136 & -2.132 & -0.173 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -0.627 & -0.042 & 3.477 & 0.242 & 0.171 & 0.011 \\ 
   \midrule 
All period & -3.032 & -0.182 & 1.893 & 0.125 & 5.116 & 0.351 & 1.860 & 0.123 \\

\midrule
\end{tabular}}

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 2.689 & 0.168 & 2.635 & 0.169 & 1.145 & 0.072 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 2.686 & 0.171 & 3.280 & 0.215 & 2.599 & 0.167 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.740 & 0.448 & 6.088 & 0.492 & 5.465 & 0.453 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 9.542 & 1.105 & 10.065 & 1.246 & 9.312 & 1.152 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -4.718 & -0.344 & -4.155 & -0.306 & -4.546 & -0.332 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -2.373 & -0.146 & -2.019 & -0.126 & -1.759 & -0.106 \\ 
   \midrule 
All period & -3.032 & -0.182 & 0.126 & 0.008 & 0.281 & 0.018 & -0.318 & -0.020 \\

\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 3.836 & 0.247 & 3.537 & 0.233 & 4.177 & 0.276 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.516 & 0.230 & 3.738 & 0.252 & 4.232 & 0.283 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.565 & 0.430 & 5.863 & 0.469 & 5.969 & 0.490 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 8.238 & 0.876 & 8.554 & 0.962 & 8.572 & 0.970 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -6.058 & -0.439 & -5.690 & -0.415 & -5.561 & -0.403 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -3.827 & -0.235 & -3.427 & -0.210 & -3.161 & -0.193 \\ 
   \midrule 
All period & -3.032 & -0.182 & -0.069 & -0.004 & -0.005 & -0.000 & 0.441 & 0.028 \\

\bottomrule
\end{tabular}}
\end{table}
